Manuscript Figures

### 2024-05-06 Manuscript_Figures.Rmd
Visualize treelist in four mapcodes

IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_df <- BA_split %>% select(MapCode,IC_ID)
F2D_df <- BA_split %>% select(MapCode,F2D_ID)
F2W_df <- BA_split %>% select(MapCode,F2W_ID)
F5D_df <- BA_split %>% select(MapCode,F5D_ID)
F5W_df <- BA_split %>% select(MapCode,F5W_ID)
Initial_map <- left_join(IC_map_df, IC_df)
F2D_map <- left_join(IC_map_df, F2D_df)
F2W_map <- left_join(IC_map_df, F2W_df)
F5D_map <- left_join(IC_map_df, F5D_df)
F5W_map <- left_join(IC_map_df, F5W_df)
IC_rst <- Initial_map %>% select(IC_ID)
F2D_rst <- F2D_map %>% select(F2D_ID)
F2W_rst <- F2W_map %>% select(F2W_ID)
F5D_rst <- F5D_map %>% select(F5D_ID)
F5W_rst <- F5W_map %>% select(F5W_ID)

Initial_map$`Initial Conditions` <- IC_rst
IC_all <- Initial_map$`Initial Conditions`
Initial_map$`Fire2-Dry` <- F2D_rst
Initial_map$`Fire2-Wet` <- F2W_rst
Initial_map$`Fire5-Dry` <- F5D_rst
Initial_map$`Fire5-Wet` <- F5W_rst
F2D_all <- Initial_map$`Fire2-Dry`
F2W_all <- Initial_map$`Fire2-Wet`
F5D_all <- Initial_map$`Fire5-Dry`
F5W_all <- Initial_map$`Fire5-Wet`
levels(IC_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2W_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5W_all) <- forest_types %>% select(FT_ID, forest_type)
before_after_all <- c(IC_all,F2D_all,F2W_all,F5D_all,F5W_all)
names(before_after_all) <- c("Initial Conditions","Fire2-Dry","Fire2-Wet","Fire5-Dry","Fire5-Wet")
```

@@

```{r}
treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run","Treelist_postlandis_cycle0.csv"))

treelist %>%
  ggplot() +
  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=1) +
  theme_bw()
#TODO: Just do a single mapcode
```

>>>>

IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_df <- BA_split %>% select(MapCode,IC_ID)
F2D_df <- BA_split %>% select(MapCode,F2D_ID)
F2W_df <- BA_split %>% select(MapCode,F2W_ID)
F5D_df <- BA_split %>% select(MapCode,F5D_ID)
F5W_df <- BA_split %>% select(MapCode,F5W_ID)

Initial_map <- left_join(IC_map_df, IC_df)
F2D_map <- left_join(IC_map_df, F2D_df)
F2W_map <- left_join(IC_map_df, F2W_df)
F5D_map <- left_join(IC_map_df, F5D_df)
F5W_map <- left_join(IC_map_df, F5W_df)

IC_rst <- Initial_map %>% select(IC_ID)
F2D_rst <- F2D_map %>% select(F2D_ID)
F2W_rst <- F2W_map %>% select(F2W_ID)
F5D_rst <- F5D_map %>% select(F5D_ID)
F5W_rst <- F5W_map %>% select(F5W_ID)

IC_map$`Initial Conditions` <- IC_rst
IC_map$`Fire2-Dry` <- F2D_rst
IC_map$`Fire2-Wet` <- F2W_rst
IC_map$`Fire5-Dry` <- F5D_rst
IC_map$`Fire5-Wet` <- F5W_rst

IC_all <- IC_map$`Initial Conditions`
F2D_all <- IC_map$`Fire2-Dry`
F2W_all <- IC_map$`Fire2-Wet`
F5D_all <- IC_map$`Fire5-Dry`
F5W_all <- IC_map$`Fire5-Wet`

levels(IC_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2W_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5W_all) <- forest_types %>% select(FT_ID, forest_type)
before_after_all <- c(IC_all,F2D_all,F2W_all,F5D_all,F5W_all)
names(before_after_all) <- c("Initial Conditions","Fire2-Dry","Fire2-Wet","Fire5-Dry","Fire5-Wet")
```

@@

```{r}
treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","Treelist_postlandis_cycle0.csv"))
set.seed = 14
sample_mapcode <- sample(unique(treelist$MapCode),1)
mapcode <- treelist %>% filter(MapCode == sample_mapcode)
mapcodes <- treelist %>%
  filter((X>=100 & X<=300) & (Y>=500 & Y<=700))

mapcodes %>%
  ggplot() +
  geom_hline(yintercept = 600, linetype = "dashed") +
  geom_vline(xintercept = 200, linetype = "dashed") +
  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
  scale_color_colorblind() +
  coord_equal() +
  labs(X = "X (m)",
       Y = "Y (m)",
       color = "Species") +
  theme_bw()
#TODO: Replace species codes with species names
```
